---
title: "Binomial Package Introduction"
author: "Jingjing Jia"
date: "04/29/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(binomial)
```


## Introduction

The binomial package facilitates binomial random variable related calculations. It includes functions for calculating the expected value, variance and other properties of a binomial random variable, as well as calculating binomial probability distributions.

We will go through functions provided in this package in the setting of tossing a loaded coin of 25% chance of heads just to give a clearer illustration of how the functions work.

## Summary Measures

The binomial package contains functions bin_mean, bin_variance, bin_mode, bin_skewness, bin_kurtosis for calculating the mean, variance, mode, skewness and kurtosis respectively of an input binomial variable. Each function takes in two inputs: trials (number of trials) and prob(the probability of success).

The expected value of heads we will get from throwing the loaded coin of 25% chance of heads can be calculated by:
```{r}
bin_mean(trials = 10, prob = 0.25)
```

<br>
The variance of the number of heads we will get can be calculated as:
```{r}
bin_variance(trials = 10, prob = 0.25)
```

Usage is the same for bin_mode, bin_skewness and bin_kurtosis.


## Binomial Variables

The package supports creating binomial variable objects. A binomial variable of the number of heads getting from toss a loaded coin with 25% chance heads 10 times can be created by:
```{r}
x <- bin_variable(trials = 10, prob = 0.25)
x
```

By calling summary on a binomial variable object, summary measures of the binomial variable will be displayed:
```{r}
x <- bin_variable(trials = 10, prob = 0.25)
summary(x)
```
where we can easily read off results that can also be calculated from functions mentioned in the previous section.

## Binomial Probabilities Related Functions

### bin_choose
First of all, we can calculate the number of ways we can get five heads from tossing the loaded coin 10 times by doing:
```{r}
bin_choose(n = 10, k = 5)
```
where the n input is for the number of trials (10 tosses of coin) and the k input for the number of successes (5 heads we want to get). So here we know there are 252 ways that we can get 5 heads of tossing a coin 10 times.


### bin_probability

Next up, we are ready to calculate some binomial probabilities. We can get the probability of getting five heads from tossing the coin 10 times by doing:
```{r}
bin_probability(success = 5, trials = 10, prob = 0.25)
```

The bin_probability function can be used to calculate probabilities for multiple number of successes at a time. For example, if we want to know the probabilities of getting 1, 2, 3 heads from tossing the loaded coin 10 times, we can simply do:
```{r}
bin_probability(success = 1:3, trials = 10, prob = 0.25)
```
where the probabilities are returned in order.


### bin_distribution
Furthermore, we can get the probabilites of all possible number of successes by using the bin_distribution function. This function simply shows the entire binomial distribution with given inputs. The following code returns an object showing the probabilities of getting 0 to 10 heads from the coin tosses.
```{r}
bin_distribution(trials = 10, prob = 0.25)
```

The binomial distribution can be illustrated visually through a barplot via the following way:
```{r}
a <- bin_distribution(trials = 10, prob = 0.25)
plot(a)
```


### bin_cumulative
bin_cumulative is one step added to bin_distribution where it also returns the cumulative probabilities. 

```{r}
bin_cumulative(trials = 10, prob = 0.25)
```
The "cumulative" column shows the probabilities of getting smaller than or equal to the corresponding number of successes.

The cumulative distribution can also be illustrated visually through a line plot as follows:
```{r}
a <- bin_cumulative(trials = 10, prob = 0.25)
plot(a)
```



